Symmetric Circuits for Rank Gates

### 2018-04-04 sections/transparency-and-unique-extensions.tex
minor revisions to Section 5.  Also inserted (informal) definition of circuit isomorphism in Sec 3 for backward reference.

\documentclass[../paper.tex]{subfiles}
\begin{document}

Many of the properties of circuits central to work of this paper, and
particularly those that reference circuit automorphisms or
syntactic-equivalence, make references to the existence of a isomorphism between
pairs of structures associated with the gates of the circuit. We recall that
each gate in a circuit is associated with a structure with the elements of the
relations of that structure labelled by the children of that gate. These
properties usually depend on the existence of an isomorphism that agrees with a
given permutation of the gates labelling the structure. This introduces a
potential difficulty as there is no know polynomial-time algorithm for the
general isomorphism problem, but we we require many of these circuit properties
to be polynomial-time decidable in order to define our translation from circuits
to formulas (see Section~\ref{sec:circuits-to-formulas}). This is not a problem
if we restrict our attention to circuits with symmetric gates, as Anderson and
Dawar~\cite{AndersonD17} do, as in this case the structures of interest are
sets, and set equivalence is clearly decidable in polynomial-time, but when we
allow for circuits to be defined over bases including non-symmetric functions it
is not obvious that these properties can be decided in polynomial-time.

@@

In the first part of this section we prove that the requisite circuit properties
are indeed polynomial-time decidable for transparent circuits. We then use these
results to define a polynomial-time computable translation from transparent
circuits to equivalent circuits with unique labels. As discussed in
Section~\ref{sec:symm-circ}, this translation allows us to restrict our
attention from transparent circuits to circuits with unique labels when working
with families of circuits without a loss of generality. This restriction is
important for two reasons. First, circuits with unique labels have unique
extensions, which enables us to apply the support theorem. Second, as we will
show in this section, all relevant symmetry-related circuit properties are
polynomial-time decidable for circuits with unique labels. We use all of these
properties in order to define our translation from circuits to formulas in
Section~\ref{sec:circuits-to-formulas}.

In the second part of this section we discuss more formally the relationship
between the problem of deciding many of these natural circuit properties and the
graph-isomorphism problem. In particular, we present reductions from the
graph-isomorphism problem to the problems of deciding each of these circuit
properties for general circuits. It follows that deciding most of these circuit
properties is hard as the graph isomorphism problem -- a problem not known to be
in $\PT$. We also show that most of these hardness results are quite robust, in
that even if we restrict our attention to other natural classes of circuits
(e.g.\ circuits with unique children or circuits with injective labels) these
decision problems remain at least as hard as the graph-isomorphism problem.
In this sense, while the first part of this section provides evidence in favour of the
sufficiency of the restriction to transparent circuits, the second part provides
evidence in favour of its necessity.

@@

\subsection{Tractable Properties of Transparent Circuits}
In the this subsection we show that many useful circuit properties are
polynomial-time decidable for transparent circuits. First, we prove that the
syntactic-equivalence relation is polynomial-time computable for transparent
circuits. We use this result to show that transparent circuits can be
transformed in polynomial-time into equivalent circuits with unique labels. We
show that for circuits with unique labels we can compute in polynomial-time the
action of a given automorphism on the circuit, the orbits and supporting
partitions of each gate, as well as the orbits and supporting partitions of each
element of the universe of each gate. We make use of all of these results in
order to define a translation from circuit families to formulas of $\FPR$ in
Section~\ref{sec:circuits-to-formulas}.

@@

  Suppose $g$ and $h$ are gates in $C$ such that $\Sigma (g) = \Sigma(h)$ and
  either both $g$ and $h$ are output gates and $\Omega^{-1}(g) = \Omega^{-1}(h)$
  or neither are output gates. Let $g$ and $h$ be input gates, then set $g
  \equiv h$ if, and only if, both $g$ and $h$ are constant gates or both are
  relational gates and $\Lambda(g) = \Lambda (h)$. Let $g$ and $h$ be internal
  gates and suppose we have defined the syntactic-equivalence relation for all
  gates of depth less than the depth of either $g$ or $h$. Then $g \equiv h$ if,
  and only if, $L(g)$ and $L(h)$ are isomorphism equivalent up to $\equiv$.

@@

  We now define a function $f: \ind(g) \rightarrow \ind(h)$ as follows. Let
  $\{x_1, \ldots, x_{\vert \ind(g)\vert}\}$ be an ordering of $\ind(g)$. For
  each $i \in \vert \ind(g) \vert$ select $y_i \in \ind(h)$ such that $y_i \neq
  y_j$ for all $j \in [i-1]$ and $L(g)(x_i) \equiv L(h)(y_i)$. If at any point
  we cannot select an appropriate $y_i$, halt and output that $g \not\equiv h$.
  For each $i \in \vert \ind(g) \vert$ let $f(x_i) = y_i$. From the definition
  of the function $f$ is injective. Check if $f$ is surjective. If not, halt and
  output that $g \not\equiv h$. We thus have that $f$ is a bijective function
  and for all $x \in \ind(g)$, $L(g)(x) \equiv L(h)(f(x))$. Check if both $g$
  and $h$ are both symmetric gates. If so, $f$ witnesses the required
  isomorphism-equivalence and so we halt and output that $g \equiv h$.

@@

It is common approach to define a new structure by \emph{quotienting} a given
structure by some equivalence relation. We now define what it means to take a
quotient of a circuit by the syntactic-equivalence relation. Intuitively, we
think of a quotient of a given circuit as being formed by `merging' each
syntactic-equivalence class into a single gate and including a wire between two
gates in the quotient circuit if, and only if, there is a wire between an
element of each equivalence class.

@@

We should note that the there is no obvious quotienting operation that
associates with each circuit a unique quotient circuit. However, it is easy to
see that if $C$ and $C'$ are distinct quotients of a given circuit then the only
point where they differ is in the definition of their respective labelling
functions. But it is not hard to see that for every gate $g$ in $C$, $L(g)$ and
$L'(g)$ are isomorphism-equivalent. It follows that these two circuits are
structurally identical in a very strong sense. Indeed, while we have not
formally defined what it means for two circuits to be isomorphic, under any
reasonable definition we would have that any two quotients of a given circuit
are isomorphic.

@@

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
  of $C$. Then $C_\equiv$ is reduced and $C$ and $C_{\equiv}$ compute the same
  function. Moreover, if $C$ is symmetric then $C_{\equiv}$ is symmetric, and
  for all $g \in G$, $g$ has unique labels in $C$ if, and only if, $[g]$ has
  unique labels in $C_{\equiv}$. In fact, for all $\sigma \in \sym_n$ if there
  exists $\pi \in \aut(C)$ extending $\sigma$ then $\pi /_\equiv$ is an
  automorphism of $C_\equiv$ extending $\sigma$.
  \label{lem:quotient-circuits-preserve}
\end{lem}
\begin{proof}
  We first prove that $C_\equiv$ and $C$ compute the same function. Let
  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
  an input gate and the result follows trivially. Suppose $g$ is an internal
  gate and suppose for all $h$ of depth less than $g$ we have that
  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from
  Lemma~\ref{lem:syntactic-equivalence-equal-function} and the inductive
  hypothesis that there exists $\lambda \in \aut(g)$ such that $L_\equiv ([g]) =
  L(g') = L(g) \lambda$. It follows from the fact that $\Sigma(g)$ is a
  structured function that $C_\equiv[\gamma \mathcal{A}]([g]) = \Sigma_\equiv
  ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g') (L^{\gamma
    \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) = \Sigma
  (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.

@@

  Let $\sigma \in \sym_n$ and suppose there exists $\pi \in \aut(C)$ extending
  $\sigma$. Let $\pi_\equiv = pi /_\equiv$. We now show that $\pi_\equiv$ is an
  automorphism of $C_\equiv$ extending $\sigma$. It is easy to see that
  $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that preserves
  syntactic-equivalence, and is thus is a well-defined function. Let $[g] \in
  G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) = \Sigma_\equiv ([\pi
  g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$. It is easy to check
  the automorphism conditions for input gates. Suppose $[g]$ is an internal
  gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g') /_\equiv$ and $h
  \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv ([\pi h]) = L(\pi h)
  /_\equiv$. We have that $\pi L(g')$ is isomorphism-equivalent to $L(\pi g')$,
  and it follows that $(\pi L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi
  g') /_\equiv$. We then have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv)
  = \pi_\equiv L_\equiv ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv
  \pi h$, we have that $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi
  h) /_\equiv = L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv
  ([g])$ is isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$.
  Suppose $[g]$ is an output gate. Then for $\vec{a} \in \dom (\Omega)$,
  $\pi_\equiv \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma
  \vec{a})] = \Omega_\equiv (\sigma \vec{a})$. It follows that if $C$ is
  symmetric then $C_\equiv$ is symmetric.

  Let $g \in G$. Suppose $[g]$ has unique labels. There exists $h \in [g]$ such
  that $L_\equiv([g]) = L(h) /_\equiv$. Since $L_\equiv([g])$ is injective,
  $L(h) /_\equiv$ must be injective and so $L(h)$ must be injective and no two
  child gates of $L(h)$ must be syntactically-equivalent. It follows that $h$
  has unique labels. Since $h \equiv g$ and $h$ has unique labels, it follows
  that $g$ has unique labels. Suppose $g$ has unique labels. Let $h \in [g]$ be
  such that $L_\equiv([g]) = L(h) /_\equiv$. Since $h \equiv g$ and $g$ has
  unique labels $h$ has unique labels and so $L_\equiv([g])$ has injective
  labels. Since each equivalence class in $C_\equiv$ is a singlton it follows
  that $[g]$ has unique labels.
\end{proof}

@@

We now show that transparent circuits can be transformed in polynomial time into
equivalent circuit with unique labels, and hence unique extensions, and that
this transformation preserves important properties.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit. There is an algorithm that that takes in such a
  circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \rho)$-circuit $C'$
  such that $C$ and $C'$ compute the same function, $C'$ has unique labels, and
  if $C$ is symmetric then $C'$ is symmetric. Moreover, this algorithm runs in
  time polynomial in the size of the input circuit.
  \label{lem:transparent-unique}
\end{lem}
\begin{proof}
  Let $C_0 := \langle G_0, \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ be the
  quotient of $C$. If $C_0$ does not contain the constant gates $g_0$ and $g_1$
  such that $\Sigma(g_0) = 0$ and $\Sigma (g_1) = 1$ we construct a new circuit
  from $C_0$ by adding gates. We abuse notation and also call this new circuit
  $C_0$. The addition of these constant gates to the circuit does not alter the
  function computed by the circuit, nor does it effect the symmetry of the
  circuit or weather it has unique labels.

@@

  Stated more informally, we define $C_1$ from $C_0$ by adding in an $\OR$-gate
  $g_\lor$ that always evaluates to one, and then adding a wire from that gate
  to all $\AND$-gates in the circuit (and also a wire from $g_\lor$ to any
  similar gate that may already exist in the circuit in order to ensure that
  $g_\lor$ is part of a singleton syntactic-equivalence class in $C_1$). The
  important point to note is that each $\AND$-gate in $C_1$ has fan-in at least
  two. We will construct $C'$ from $C_1$ by adding in a number of $\AND$-gates
  with fan-in one. Therefore, since all of the $\AND$-gates in $C_1$ have fan-in
  two, it will follow that none of these new gates are syntactically-equivalent
  to any gate in $C_1$. We now show that $C_1$ and $C_0$ compute the same
  function and if $C_0$ is symmetric then $C_1$ is symmetric.

@@

    Suppose $g \in G_{\land}$. Then there exists $h \in G_1$ and $i \in [c^h -
    1]$ such that $g = g^h_i$. Suppose $g' \in G_1$. Then $\Sigma'(g) =
    \AND[1]$. But, from the construction of $C_1$, there are no single-input
    $\AND$-gates in $G_1$. It follows $\Sigma'(g') \neq \Sigma'(g)$ and so $g'
    \not\equiv' g$, a contradiction, and so we must have $g' \in G_{\land}$. If
    $i = 1$ then $\{ h \} = H_g' = H_{g'}'$. Since the only gate in $G_\land$
    that has $h$ as a child gate is $g^h_1$, it follows that $g = g^h_1 = g'$.
    If $i > 1$ then $\{g^{h}_{i-1}\} = H_g' = H_{g'}'$. Since $g^h_i$ is the
    only gate in $G_\land$ that has $g^h_{i-1}$ as a child gate, we have $g =
    g^h_i = g'$. It follows that if $g \in G_\land$ then $g = g'$.

@@

  \begin{claim}
    Let $g \in G_1$, $\mathcal{A}$ be a $\rho$-structure of size $n$, and
    $\gamma$ be a bijection from the universe of $\mathcal{A}$ to $[n]$. Then
    $C'[\gamma \mathcal{A}](g) = C_1[\gamma \mathcal{A}](g)$.
  \end{claim}
  \begin{proof}
    It is easy to see that for all $h \in G_1$ and $i \in [c^h-1]$ we have that
    $C'[\gamma \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h)$. Suppose $g \in
    G_1$. We now prove the result by induction on the depth of a gate. Suppose
    $g$ has depth $0$. In this case $g$ is an input gate, and the result follows
    trivially. Suppose $g$ is an internal gate, and for all $h$ of depth less
    than $g$ we have that if $h \in G_1$ then $C'[\gamma \mathcal{A}](h) =
    C_1[\gamma \mathcal{A}](h)$. Let $x \in \ind(g)$. Recall that $C'$ is
    constructed such that if $g \in G_1$ then for all $x \in \ind(g)$ and $h \in
    H_g$, $L_1(g)(x) = h$ if, and only if, $L'(g)(x) \in \{h, g^h_1, \ldots ,
    g^h_{c^h_g - 1}\}$. But, from the construction, we have that all of the
    gates in $\{h, g^h_1, \ldots, g^h_{c^h_g -1}\}$ evaluate to the same value
    for a given input to the circuit. Thus, from the inductive hypothesis, we
    have that if $L'(g)(x) \in G_1$ then $ {L'}^{\gamma \mathcal{A}}(g)(x) =
    C'[\gamma \mathcal{A}](L(g)(x)) = C_1[\gamma \mathcal{A}](L_1(g)(x)) =
    L^{\gamma \mathcal{A}}_1(g)(x) $. If $L'(g)(x) \not\in G_1$ then $L'(g)(x)
    \in G_{\land}$ and so $L'(g)(x) = g^h_i$, where $h = L_1(g)(x)$ and some $i
    \in [c^h_g -1]$. But then ${L'}^{\gamma \mathcal{A}}(g)(x) = C'[\gamma
    \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h) = C_1[\gamma \mathcal{A}](h)
    = L^{\gamma \mathcal{A}}_1(g)(x)$. The penultimate equality follow from from
    the inductive hypothesis. The final equality follows from the fact that $h =
    L_1 (g)(x)$. We thus have $C'[\gamma \mathcal{A}](g) = \Sigma'({L'}^{\gamma
      \mathcal{A}}(g)) = \Sigma_1 (L^{\gamma \mathcal{A}}_1(g)) = C_1[\gamma
    \mathcal{A}](g)$.
  \end{proof}

>>>>

\documentclass[../paper.tex]{subfiles}
\begin{document}
Recall that each gate $g$ in a cricuit  is associated with a structure
$D$ with the elements of the relations in $D$, i.e.\ $\ind(\Sigma(g))$
labelled by the children of $g$.  Many of the properties of circuits
that are central to our construction, and we wish to be able to decide
efficiently, particularly those that reference circuit automorphisms or
syntactic-equivalence, depend on the existence of isomorphisms that agrees with a
given permutation of the gates labelling the structure.  This introduces a
potential difficulty as there is no known polynomial-time algorithm for the
general isomorphism problem, but we we require many of these circuit properties
to be polynomial-time decidable in order to define our translation from circuits
to formulas (see Section~\ref{sec:circuits-to-formulas}).  This is not a problem
if we restrict our attention to circuits with symmetric gates, as
in~\cite{AndersonD17}, as in this case the structures of interest are
sets, and set equivalence is clearly decidable in polynomial-time.  When we
allow for circuits to be defined over bases including non-symmetric functions it
is not obvious that these properties can be decided in polynomial-time.

@@

In the first part of this section we prove that the requisite circuit properties
are indeed polynomial-time decidable for transparent circuits. We then use these
results to define a polynomial-time computable translation from transparent
circuits to equivalent circuits with unique labels. As discussed in
Section~\ref{sec:symm-circ}, this translation allows us to restrict our
attention from transparent circuits to circuits with unique labels when working
with families of circuits without a loss of generality. This restriction is
important for two reasons. First, circuits with unique labels have unique
extensions, which enables us to apply the support theorem. Second, as we
show in this section, all relevant symmetry-related circuit properties are
polynomial-time decidable for circuits with unique labels. We use all of these
properties in order to define our translation from circuits to formulas in
Section~\ref{sec:circuits-to-formulas}.

In Section~\ref{sec:necessity} we discuss more formally the relationship
between the problem of deciding many of these natural circuit properties and the
graph-isomorphism problem. In particular, we present reductions from the
graph-isomorphism problem to the problems of deciding each of these circuit
properties for general circuits. It follows that deciding most of these circuit
properties is as hard as the graph isomorphism problem---a problem not known to be
in $\PT$, showing that some condition like transparency is necessary.  We also show that most of these hardness results are quite robust, in
that even if we restrict our attention to other natural classes of circuits
(e.g.\ circuits with unique children or circuits with injective labels) these
decision problems remain at least as hard as the graph-isomorphism problem.
In this sense, while the first part of this section provides evidence in favour of the
sufficiency of the restriction to transparent circuits, the second part provides
evidence in favour of its necessity.

@@

\subsection{Tractable Properties of Transparent Circuits}
In this subsection we show that many useful circuit properties are
polynomial-time decidable for transparent circuits. First, we prove that the
syntactic-equivalence relation is polynomial-time computable for transparent
circuits. We use this result to show that transparent circuits can be
transformed in polynomial-time into equivalent circuits with unique labels. We
show that for circuits with unique labels we can compute in polynomial-time the
action of a given automorphism on the circuit, the orbits and supporting
partitions of each gate, as well as the orbits and supporting partitions of each
element of the universe of each gate. We make use of all of these results in
order to define a translation from circuit families to formulas of $\FPR$ in
Section~\ref{sec:circuits-to-formulas}.

@@

  Suppose $g$ and $h$ are gates in $C$ such that $\Sigma (g) = \Sigma(h)$ and
  either both $g$ and $h$ are output gates and $\Omega^{-1}(g) = \Omega^{-1}(h)$
  or neither are output gates. Let $g$ and $h$ be input gates, then set $g
  \equiv h$ if, and only if, both $g$ and $h$ are constant gates or both are
  relational gates and $\Lambda(g) = \Lambda (h)$. Let $g$ and $h$ be internal
  gates and suppose we have defined the syntactic-equivalence relation for all
  gates of depth less than the depth of either $g$ or $h$. Then $g \equiv h$ if,
  and only if, $L(g)$ and $L(h)$ are isomorphic up to $\equiv$.

@@

  We now define a function $f: \ind(g) \rightarrow \ind(h)$ as follows. Let
  $\{x_1, \ldots, x_{\vert \ind(g)\vert}\}$ be an ordering of $\ind(g)$. For
  each $i \in \vert \ind(g) \vert$ select $y_i \in \ind(h)$ such that $y_i \neq
  y_j$ for all $j \in [i-1]$ and $L(g)(x_i) \equiv L(h)(y_i)$. If at any point
  we cannot select an appropriate $y_i$, halt and output that $g \not\equiv h$.
  For each $i \in \vert \ind(g) \vert$ let $f(x_i) = y_i$. From the definition
  of the function $f$ is injective. Check if $f$ is surjective. If not, halt and
  output that $g \not\equiv h$. We thus have that $f$ is a bijective function
  and for all $x \in \ind(g)$, $L(g)(x) \equiv L(h)(f(x))$. Check if $g$
  and $h$ are both symmetric gates. If so, $f$ witnesses the required
  isomorphism-equivalence and so we halt and output that $g \equiv h$.

@@

 We now define what it means to take a
quotient of a circuit by the syntactic-equivalence relation. Intuitively, we
think of a quotient of a given circuit as being formed by `merging' each
syntactic-equivalence class into a single gate and including a wire between two
gates in the quotient circuit if, and only if, there is a wire between an
element of each equivalence class.

@@

We should note that the there is no obvious quotienting operation that
associates with each circuit a unique quotient circuit. However, it is easy to
see that if $C$ and $C'$ are distinct quotients of a given circuit then the only
point where they differ is in the definition of their respective labelling
functions. But it is not hard to see that for every gate $g$ in $C$, $L(g)$ and
$L'(g)$ are isomorphic.  It follows that these two circuits are
isomorphic in the precise sense alluded to right after Definition~\ref{defn:automorphism}.

@@

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L\rangle$ be a $(\BB,
  \rho)$-circuit of order $n$ and $C_{\equiv} = \langle G_\equiv ,
  \Omega_\equiv, \Sigma_\equiv , \Lambda_\equiv, L_\equiv \rangle$ be a quotient
  of $C$. Then $C_\equiv$ is reduced and $C$ and $C_{\equiv}$ compute the same
  function. Moreover, if $C$ is symmetric then $C_{\equiv}$ is symmetric, and
  for all $g \in G$, $g$ has unique labels in $C$ if, and only if, $[g]$ has
  unique labels in $C_{\equiv}$.  Indeed, for all $\sigma \in \sym_n$ if there
  exists $\pi \in \aut(C)$ extending $\sigma$ then $\pi /_\equiv$ is an
  automorphism of $C_\equiv$ extending $\sigma$.
  \label{lem:quotient-circuits-preserve}
\end{lem}
\begin{proof}
  We first prove that $C_\equiv$ and $C$ compute the same function. Let
  $\mathcal{A}$ be a $\rho$-structure of size $n$ and let $\gamma$ be a
  bijection from $U$ to $[n]$. We now show that for all $g \in G$, $C_\equiv
  [\gamma \mathcal{A}]([g]) = C[\gamma \mathcal{A}](g)$. We do this by induction
  on the depth of a gate. Suppose $g \in G$ has depth $0$. In this case $g$ is
  an input gate and the result follows trivially. Suppose $g$ is an internal
  gate and suppose for all $h$ of depth less than $g$ we have that
  $C_\equiv[\gamma \mathcal{A}]([h]) = C[\gamma \mathcal{A}](h)$. We have that
  there exists $g' \in [g]$ such that $L_\equiv ([g]) = L(g') /_\equiv$ and
  $\Sigma_\equiv([g]) = \Sigma (g) = \Sigma (g')$. We have from
  Lemma~\ref{lem:syntactic-equivalence-equal-function} and the inductive
  hypothesis that there exists $\lambda \in \aut(g)$ such that $L_\equiv ([g]) =
  L(g') = L(g) \lambda$. It follows from the fact that $\Sigma(g)$ is a
  structured function that $C_\equiv[\gamma \mathcal{A}]([g]) = \Sigma_\equiv
  ([g])(L^{\gamma \mathcal{A}}_\equiv([g])) = \Sigma (g') (L^{\gamma
    \mathcal{A}}(g')) = \Sigma (g)(L^{\gamma \mathcal{A}}(g) \lambda) = \Sigma
  (g) (L^{\gamma \mathcal{A}}(g)) = C[\gamma \mathcal{A}](g)$.

@@

  Let $\sigma \in \sym_n$ and suppose there exists $\pi \in \aut(C)$ extending
  $\sigma$. Let $\pi_\equiv = \pi /_\equiv$. We now show that $\pi_\equiv$ is an
  automorphism of $C_\equiv$ extending $\sigma$. It is easy to see that
  $\pi_\equiv$ is a bijection from $G_\equiv$ to $G_\equiv$ that preserves
  syntactic-equivalence, and is thus is a well-defined function. Let $[g] \in
  G_\equiv$. We have that $\Sigma_\equiv (\pi_\equiv [g]) = \Sigma_\equiv ([\pi
  g]) = \Sigma (\pi g) = \Sigma (g) = \Sigma_\equiv ([g])$. It is easy to check
  the automorphism conditions for input gates. Suppose $[g]$ is an internal
  gate. Let $g' \in [g]$ be such that $L_\equiv([g]) = L(g') /_\equiv$ and $h
  \in [g]$ be such that $L_\equiv(\pi_\equiv[g]) = L_\equiv ([\pi h]) = L(\pi h)
  /_\equiv$. We have that $\pi L(g')$ is isomorphism-equivalent to $L(\pi g')$,
  and it follows that $(\pi L(g'))/_\equiv$ is isomorphism-equivalent to $L(\pi
  g') /_\equiv$. We then have $(\pi L(g'))/_\equiv = \pi_\equiv (L(g') /_\equiv)
  = \pi_\equiv L_\equiv ([g])$ and, since $g' \equiv h$ and so $\pi g' \equiv
  \pi h$, we have that $L(\pi g')/_\equiv$ is isomorphism-equivalent to $L(\pi
  h) /_\equiv = L_\equiv(\pi_\equiv[g])$. It follows that $\pi_\equiv L_\equiv
  ([g])$ is isomorphism-equivalent to $L_\equiv(\pi_\equiv [g]) /_\equiv$.
  Suppose $[g]$ is an output gate. Then for $\vec{a} \in \dom (\Omega)$,
  $\pi_\equiv \Omega_\equiv (\vec{a}) = [\pi \Omega (\vec{a})] = [\Omega (\sigma
  \vec{a})] = \Omega_\equiv (\sigma \vec{a})$. It follows that if $C$ is
  symmetric then $C_\equiv$ is symmetric.

  Let $g \in G$. Suppose $[g]$ has unique labels. There exists $h \in [g]$ such
  that $L_\equiv([g]) = L(h) /_\equiv$. Since $L_\equiv([g])$ is injective,
  $L(h) /_\equiv$ must be injective and so $L(h)$ must be injective and no two
  child gates of $L(h)$ must be syntactically-equivalent. It follows that $h$
  has unique labels. Since $h \equiv g$ and $h$ has unique labels, it follows
  that $g$ has unique labels. Suppose $g$ has unique labels. Let $h \in [g]$ be
  such that $L_\equiv([g]) = L(h) /_\equiv$. Since $h \equiv g$ and $g$ has
  unique labels $h$ has unique labels and so $L_\equiv([g])$ has injective
  labels. Since each equivalence class in $C_\equiv$ is a singleton it follows
  that $[g]$ has unique labels.
\end{proof}

@@

We now show that transparent circuits can be transformed in polynomial time into
equivalent circuits with unique labels, and hence unique extensions, and that
this transformation preserves important properties.

\begin{lem}
  Let $C := \langle G, \Omega, \Sigma, \Lambda, L \rangle$ be a transparent
  $(\mathbb{B}, \rho)$-circuit. There is an algorithm that takes in such a
  circuit and outputs a $(\mathbb{B} \cup \mathbb{B}_{\std}, \rho)$-circuit $C'$
  such that $C$ and $C'$ compute the same function, $C'$ has unique labels, and
  if $C$ is symmetric then $C'$ is symmetric. Moreover, this algorithm runs in
  time polynomial in the size of the input circuit.
  \label{lem:transparent-unique}
\end{lem}
\begin{proof}
  Let $C_0 := \langle G_0, \Omega_0, \Sigma_0, \Lambda_0, L_0 \rangle$ be the
  quotient of $C$. If $C_0$ does not contain the constant gates $g_0$ and $g_1$
  such that $\Sigma(g_0) = 0$ and $\Sigma (g_1) = 1$ we construct a new circuit
  from $C_0$ by adding gates. We abuse notation and also call this new circuit
  $C_0$. The addition of these constant gates to the circuit does not alter the
  function computed by the circuit, nor does it effect the symmetry of the
  circuit or weather it has unique labels.

@@

  Stated more informally, we define $C_1$ from $C_0$ by adding in an $\OR$-gate
  $g_\lor$ that always evaluates to one, and then adding a wire from that gate
  to all $\AND$-gates in the circuit (and also a wire from $g_\lor$ to any
  similar gate that may already exist in the circuit in order to ensure that
  $g_\lor$ is part of a singleton syntactic-equivalence class in $C_1$). The
  important point to note is that each $\AND$-gate in $C_1$ has fan-in at least
  two. We construct $C'$ from $C_1$ by adding in a number of $\AND$-gates
  with fan-in one. Therefore, since all of the $\AND$-gates in $C_1$ have fan-in
  two, it follows that none of these new gates are syntactically-equivalent
  to any gate in $C_1$. We now show that $C_1$ and $C_0$ compute the same
  function and if $C_0$ is symmetric then $C_1$ is symmetric.

@@

    Suppose $g \in G_{\land}$. Then there exists $h \in G_1$ and $i \in [c^h -
    1]$ such that $g = g^h_i$. Suppose $g' \in G_1$. Then $\Sigma'(g) =
    \AND[1]$. But, from the construction of $C_1$, there are no single-input
    $\AND$-gates in $G_1$. It follows $\Sigma'(g') \neq \Sigma'(g)$ and so $g'
    \not\equiv' g$, a contradiction, and so we must have $g' \in G_{\land}$. If
    $i = 1$ then $\{ h \} = H_g' = H_{g'}'$.  Since the only gate in $G_\land$
    that has $h$ as a child is $g^h_1$, it follows that $g = g^h_1 = g'$.
    If $i > 1$ then $\{g^{h}_{i-1}\} = H_g' = H_{g'}'$. Since $g^h_i$ is the
    only gate in $G_\land$ that has $g^h_{i-1}$ as a child, we have $g =
    g^h_i = g'$. It follows that if $g \in G_\land$ then $g = g'$.

@@

  \begin{claim}
    Let $g \in G_1$, $\mathcal{A}$ be a $\rho$-structure of size $n$, and
    $\gamma$ be a bijection from the universe of $\mathcal{A}$ to $[n]$. Then
    $C'[\gamma \mathcal{A}](g) = C_1[\gamma \mathcal{A}](g)$.
  \end{claim}
  \begin{proof}
    It is easy to see that for all $h \in G_1$ and $i \in [c^h-1]$ we have that
    $C'[\gamma \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h)$. Suppose $g \in
    G_1$. We now prove the result by induction on the depth of a gate. Suppose
    $g$ has depth $0$. In this case $g$ is an input gate, and the result follows
    trivially. Suppose $g$ is an internal gate, and for all $h$ of depth less
    than $g$ we have that if $h \in G_1$ then $C'[\gamma \mathcal{A}](h) =
    C_1[\gamma \mathcal{A}](h)$. Let $x \in \ind(g)$. Recall that $C'$ is
    constructed such that if $g \in G_1$ then for all $x \in \ind(g)$ and $h \in
    H_g$, $L_1(g)(x) = h$ if, and only if, $L'(g)(x) \in \{h, g^h_1, \ldots ,
    g^h_{c^h_g - 1}\}$. But, from the construction, we have that all of the
    gates in $\{h, g^h_1, \ldots, g^h_{c^h_g -1}\}$ evaluate to the same value
    for a given input to the circuit. Thus, from the inductive hypothesis, we
    have that if $L'(g)(x) \in G_1$ then $ {L'}^{\gamma \mathcal{A}}(g)(x) =
    C'[\gamma \mathcal{A}](L(g)(x)) = C_1[\gamma \mathcal{A}](L_1(g)(x)) =
    L^{\gamma \mathcal{A}}_1(g)(x) $. If $L'(g)(x) \not\in G_1$ then $L'(g)(x)
    \in G_{\land}$ and so $L'(g)(x) = g^h_i$, where $h = L_1(g)(x)$ and some $i
    \in [c^h_g -1]$. But then ${L'}^{\gamma \mathcal{A}}(g)(x) = C'[\gamma
    \mathcal{A}](g^h_i) = C'[\gamma \mathcal{A}](h) = C_1[\gamma \mathcal{A}](h)
    = L^{\gamma \mathcal{A}}_1(g)(x)$. The penultimate equality follow from 
    the inductive hypothesis. The final equality follows from the fact that $h =
    L_1 (g)(x)$. We thus have $C'[\gamma \mathcal{A}](g) = \Sigma'({L'}^{\gamma
      \mathcal{A}}(g)) = \Sigma_1 (L^{\gamma \mathcal{A}}_1(g)) = C_1[\gamma
    \mathcal{A}](g)$.
  \end{proof}

  Since $\Omega' = \Omega_1$, we have that $C'$ and $C_1$ compute the same
  function. It follows that, since $C_1$ and $C$ compute the same function, $C$
  and $C'$ compute the same function. Since $C$ is transparent, we may construct
  the quotient circuit $C_0$ in time polynomial in $\vert C \vert$. Since $C_1$
  is constructed by adding in a single gate and then adding at most $\vert C_0
  \vert$ wires, we may construct $C_1$ from $C_0$ in time polynomial in $\vert C
  \vert$. It is easy to see that $C'$ can be constructed in time polynomial
  in $\vert C_1 \vert$ and hence polynomial in $\vert C \vert$. The result
  follows.
  %
  % It is easy to see that $C'$ has injective labels. Let $g$ be an internal
  % gate
  % in $C'$ and suppose each gate of depth less than $g$ has unique labels. Let
  % $h, h' \in H_g$ such that $h \equiv h'$. If $h, h' \in G_1$ it follows $h =
  % h'$. Suppose $h, h' \in G_{\land}$. Then there exists $d, d' \in G_1$ and
  % $i,
  % j$ such that $g^d_i \equiv g^{d'}_j$. If $j = i$ then $d \equiv d'$ and so
  % $d
  % = d'$ and $h = h'$. Suppose, without a loss of generality, that $i > j$. It
  % follows that $g^d_{i-j} \equiv d'$. But then $d'$ is a single-input
  % $\AND$-gate, which is impossible, as from the construction $d'$ must have at
  % least two inputs. Suppose
